Embedding Dimension of Polyhedral Losses

### 2020-06-09 colt-20/embed-dim.tex
Small tweaks addressing some comments

\subsection{Related work}
\citet{zhang2004convex,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
%, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
	A loss $L: \reals^d \to \nonnegreals^{\Y}$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (piecewise linear convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

% \paragraph{Properties of distributions.}
In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
%% Bo: since we use \gamma and \R for \ell, and we use \Gamma and \reals^d for L,
%% I figured generic properties could use notation g and R for f
\begin{definition}[(Finite) property, level set, elicited]\jessiet{Bo in FIXME: Change $\R$ since this is the only place $\R$ is not finite?}\jessiet{Changed $\R$ to $\R'$?}
  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R'}$ for some set $\R'$ where $\Gamma(p) \neq \emptyset$ for all $p$.
  It is \emph{finite} if $|\R'| < \infty$.
  The \emph{level set} of $r \in \R'$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
  A loss function $L: \R' \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R'} \inprod{p}{L(r)}$.
\end{definition}
In this paper we write $\ell$ for discrete losses (i.e., when $|\R|$ is finite), and $\gamma$ instead of $\Gamma$ for the property elicited by $\ell$, reserving $\Gamma$ and $L$ for properties and losses on report space $\R=\reals^d$.
For example, 0-1 loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
Notice in this example $\gamma(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
%Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e. ties must be broken in all possible ways).

>>>>

\subsection{Related work}
\citet{zhang2004statistical,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
%, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
	A loss $L: \reals^d \to \nonnegreals^{\Y}$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (piecewise linear convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.
% \paragraph{Properties of distributions.}
In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
%% Bo: since we use \gamma and \R for \ell, and we use \Gamma and \reals^d for L,
%% I figured generic properties could use notation g and R for f
\begin{definition}[(Finite) property, level set, elicited]
  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R'}$ for some set $\R'$ where $\Gamma(p) \neq \emptyset$ for all $p$.
  It is \emph{finite} if $|\R'| < \infty$.
  The \emph{level set} of $r \in \R'$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
  A loss function $L: \R' \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R'} \inprod{p}{L(r)}$.
\end{definition}
In this paper we write $\ell$ for discrete losses (i.e., when $|\R|$ is finite), and $\gamma$ instead of $\Gamma$ for the property elicited by $\ell$, reserving $\Gamma$ and $L$ for properties and losses on report space $\R=\reals^d$.
For example, 0-1 loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
Notice in this example $\gamma(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
%Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e. ties must be broken in all possible ways).
